Blas\'e3D

### 2023-10-10 paper/paper2/ms.tex
Pair coding V3
Neat ideas for repittion of a flowchart!
Pair coding V5

@@

\begin{mdframed}
    \textbf{Line property trends across the grid}
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

@@

\begin{mdframed}
    \textbf{Line-by-Line Parameter Surfaces}

>>>>

\begin{mdframed}
    \textbf{Figure: Flowchart-with-words}
\end{mdframed}

@@

\begin{mdframed}
    \textbf{Line property bulk trends across the grid}
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

@@

\begin{mdframed}
    \textbf{Anomalies in Heatmaps}
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

\section{Mapping Line Parameters to Fundamental Properties}
\begin{mdframed}
    \textbf{Statement: A Bidirectonal Relation exists}
    - Goal: identify a functional form
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

\begin{mdframed}
    \textbf{Figure: Flowchart-with-equations}
\end{mdframed}

\begin{mdframed}
    \textbf{Functional Form}
    - Describe functional form options and refinement procedures
    - List possibilities, Linreg, GPs, NNs, etc.
    - We choose LSTSQ
    - Enumerate functional form
    - Adapting model complexity
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

\begin{mdframed}
    \textbf{Address what to do with missing lines}
    \textcolor{lightgray}{\blindtext}
\end{mdframed}
